---
title: "mlr3hf: Using Hugging Face Datasets in mlr3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mlr3hf: Using Hugging Face Datasets in mlr3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(mlr3hf)
library(mlr3)
```

# Introduction

The `mlr3hf` package provides a simple interface to load datasets
from the Hugging Face Hub and convert them into `mlr3` Tasks.

This allows users to directly use Hugging Face tabular datasets
within the `mlr3` machine learning ecosystem.

# How `htsk()` Works

The `htsk()` function performs the following steps:

1. Downloads a dataset file from Hugging Face Hub.
2. Loads the file into R as a `data.frame`.
3. Detects the target column type.
4. Creates either:
   - `TaskClassif` (for classification)
   - `TaskRegr` (for regression)

# Classification Example

We load a tabular dataset hosted on Hugging Face:
```{r}
task <- htsk(
  repo_id = "a4n9i/iris-tabular",
  filename = "iris.csv",
  target = "Species"
)

task
```

Now we train a simple decision tree:
```{r}
if (requireNamespace("rpart", quietly = TRUE)) {
  learner <- lrn("classif.rpart")
  learner$train(task)
}
```

# Regression Example

Assume we have a dataset with numeric target:
```r
task_regr <- htsk(
  repo_id = "username/housing-data",
  filename = "housing.csv",
  target = "price"
)
```

Then:
```r
learner <- lrn("regr.lm")
learner$train(task_regr)
```

# Limitations

Currently, `mlr3hf`:

- Supports tabular datasets only (CSV, JSON, Parquet, RDS).
- Requires explicit `target` column specification.
- Does not support Hugging Face `datasets` library format.
- Does not support image or text tokenized datasets.

# Conclusion

`mlr3hf` provides a minimal and clean bridge between
Hugging Face Hub datasets and the mlr3 framework.